An Adolescent Mini-Neptune in the Kepler Field

### 2021-08-16 paper/ms.tex
update ms

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet.  The utility
of this element for age dating young stars has been reviewed by
\citet{soderblom_ages_2014}.  We acquired an iodine-free spectrum from
Keck/HIRES on the night of 26 March 2021 using the standard setup and
reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we measure ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}\,$m\AA.   Note that this value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Given the stellar
parameters of \sn\ (Table~\ref{tab:starparams}), most notably its
effective temperature, this measurement is also in agreement with an
age for the star between 30\,Myr and 50\,Myr (see {\it e.g.}, Figure~9
of \citealt{bouma_2021_ngc2516}, or the data from
\citealt{randich_gaiaeso_2018}).

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local slope
    of the light curve.  The two quantities appear anti-correlated,
    which is most easily explained by starspot crossings during the
    first (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa are most easily understood by considering
    that the flux from the star changes by $\sim$60\,ppt per half
    rotation period ($\sim$1.3\,days).
    {\it Bottom:} Keck/HIRES transit of 7 Aug 2021 UT, observed
    simultaneously with MUSCAT3.  A quadratic baseline trend was
    allowed in the fit.  The best-fit sky-projected obliquity in this
    model is listed in red; the detection however has marginal
    statistical significance compared to a ``trend-only'' model.
    \label{fig:obliquity}
	}
\end{figure}

@@

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, which we parametrized
with three parameters: the sky-projected obliquity, the stellar
equatorial velocity, and the gaussian dispersion of spectral lines.
We then allowed for a linear and optionally quadratic trend, along
with a white-noise jitter term.  The quadratic model with the RM
effect is shown in Figure~\ref{fig:obliquity}.  We found $\chi^2_{\rm
red} = 5.4$ for the best-fitting linear case, and $\chi^2_{\rm red} =
4.4$ for the best-fitting quadratic, with a $\Delta {\rm BIC} = {\rm
BIC}_{\rm lin} - {\rm BIC}_{\rm quad} = 19.6$ and $\Delta {\rm AIC} =
{\rm AIC}_{\rm lin} - {\rm AIC}_{\rm quad} = 20.6$.  While this
provides strong statistical evidence to prefer the quadratic model
over the linear one, the $\chi^2_{\rm red}$ indicate that neither fit
is particularly good.  Considering a quadratic trend alone without any
RM effect yields $\chi^2_{\rm red} = 4.3$, and $\Delta {\rm BIC} =
{\rm BIC}_{\rm trend} - {\rm BIC}_{\rm quad} = 1.9$ (similarly $\Delta
{\rm AIC}=5.2$); from a model-comparison standpoint, there is only
weak statistical evidence to prefer the best-fitting ``RM and
quadratic trend'' model over the best-fitting ``quadratic trend only''
model.  Given the expected semi-amplitude of the velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$) and the actual achieved
precision, the claim of having ``detected the Doppler
transit'' is therefore marginal.  Observationally however, we
know from the MUSCAT3 data that the transit was observed, and the
increase in radial velocity observed shortly after ingress is more
consistent with a prograde or polar orbit than a retrograde one.
Fixing the orbit to be either exactly prograde or exactly retrograde
and allowing for a quadratic trend, we find $\Delta {\rm BIC} = {\rm
BIC}_{\rm retrograde} - {\rm BIC}_{\rm prograde} = 20.4$; the
retrograde case is ruled out on this basis.  More precise data will
however still be useful to make a more precise obliquity measurement.

>>>>

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet.  The utility
of this element for age dating young stars has been reviewed by
\citet{soderblom_ages_2014}.  We acquired an iodine-free spectrum from
Keck/HIRES on the night of 26 March 2021 using the standard setup and
reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}\,$m\AA.   Note that this value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Given the stellar
parameters of \sn\ (Table~\ref{tab:starparams}), most notably its
effective temperature, this measurement is also in agreement with an
age for the star between 30\,Myr and 50\,Myr (see {\it e.g.}, Figure~9
of \citealt{bouma_2021_ngc2516}, or the data from
\citealt{randich_gaiaeso_2018}).

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local slope
    of the light curve.  The two quantities appear anti-correlated,
    which is most easily explained by starspot crossings during the
    first (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa are most easily understood by considering
    that the flux from the star changes by $\sim$60\,ppt per half
    rotation period ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities from
    Keck/HIRES during a transit on 7 Aug 2021 UT, observed
    simultaneously with MUSCAT3 ({\it griz} photometry).  A quadratic baseline trend was
    allowed in the RV fit.  The best-fit sky-projected obliquity in this
    model is listed in red; the detection however has marginal
    statistical significance compared to a ``trend-only'' model.
    \label{fig:obliquity}
	}
\end{figure}

@@

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, and allowed three parameters
to vary: the sky-projected obliquity, the stellar
equatorial velocity, and the Gaussian dispersion of spectral lines.
We also allowed for an optional linear and quadratic trend, and
a white-noise jitter term.  The quadratic model with the RM
effect is shown in Figure~\ref{fig:obliquity}.  We found $\chi^2_{\rm
red} = 5.4$ for the best-fitting linear case, and $\chi^2_{\rm red} =
4.4$ for the best-fitting quadratic, with a $\Delta {\rm BIC} = {\rm
BIC}_{\rm line} - {\rm BIC}_{\rm quad} = 19.6$ and $\Delta {\rm AIC} =
{\rm AIC}_{\rm line} - {\rm AIC}_{\rm quad} = 20.6$.  While this
provides strong statistical evidence to prefer the quadratic model
over the linear one, the $\chi^2_{\rm red}$ indicate that neither fit
is particularly good.  Considering a quadratic trend alone without any
RM effect yields $\chi^2_{\rm red} = 4.3$, and $\Delta {\rm BIC} =
{\rm BIC}_{\rm trend} - {\rm BIC}_{\rm quad} = 1.9$ (similarly $\Delta
{\rm AIC}=5.2$); from a model-comparison standpoint, there is therefore only
weak statistical evidence to prefer the best-fitting ``RM and
quadratic trend'' model over the best-fitting ``quadratic trend only''
model.  Given the expected semi-amplitude of the velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$) and the actual achieved
precision, the claim of having detected the Doppler
transit is therefore marginal.  
From the MUSCAT3 data however, we do know that the transit was observed, and the
increase in radial velocity seen shortly after ingress is more
consistent with a prograde or polar orbit than a retrograde one.
Fixing the orbit to be either exactly prograde or exactly retrograde
and allowing for a quadratic trend, we find $\Delta {\rm BIC} = {\rm
BIC}_{\rm retrograde} - {\rm BIC}_{\rm prograde} = 20.4$; the
retrograde case is ruled out on this basis.  More precise data will
however still be useful to make a more precise obliquity measurement.
